---
title: "R Tutorial 3"
author: "Jose Zayas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r libraries}
library(ggplot2)
```

# Assignment 3: GGPLOT

### Q1. Create a histogram showing the distribution of Girth.

```{r}
data("trees")

hist(trees$Girth,
main = "Distribution of Girth",
xlab = "Girth",
col = "lightblue",
border = "white",
)
```

<br>

### Q2. Create a histogram showing the distribution of Volume.

```{r}
data("trees")

hist(trees$Volume,
main = "Distribution of Volume",
xlab = "Girth",
col = "red",
border = "white",
)
```

<br>

### Q3. Create a scatterplot showing the relationship between Girth and Volume.

```{r}
data(trees)
# Create a line chart
plot <- plot(
  trees$Girth ~ trees$Volume,
  type = "p",                      # line plot
  col = "gold",                    # line color
  lwd = 2,                         # line width
  xlab = "Girth",  # x-axis label
  ylab = "Volume", # y-axis label
  main = "Relationship between Girth and Volume"
)
```

<br>

### Q4. Use the Shapiro–Wilk test to assess whether Volume is normally distributed. Report the p-value and state whether the data are normally distributed.

```{r}
shapiro.test(trees$Volume)
```

#### - The data are NOT normally distributed. There is statistically significant evidence that Volume deviates from a normal distribution.

<br>

### Q5. Repeat the Shapiro–Wilk test for Girth. Report the p-value and state whether Girth is normally distributed.

```{r}
shapiro.test(trees$Girth)
```
#### - The data are normally distributed. The Shapiro–Wilk test does not detect a significant departure from normality for Girth

